Refunctionalization of Abstracting Abstract Machines (Functional Pearl)

### 2018-03-16 paper.tex
Outline

The paper is organized as follows.

In section \ref{background}, we first describe the target language we will
analyze and a concrete CESK machine as small-step operational semantics for it.
Then we review abstracting abstract machines (AAM) as an abstract interpretation
counterpart of CESK machines. In section \ref{linear}, we convert the
non-deterministic choices of closures to another layer of continuations,
therefore linearize the abstract execution.
Section \ref{fusing} fuses the driver function and step function to one single
function.
In section \ref{disen}, we further identify the first-order data type representations of
continuations, and disentangle the code blocks for dispatching data types to separate
functions.
Section \ref{refunc} represents the refunctionalized abstract abstract machines,
In this part, the continuations represented by data type turn to higher-order
functions.
In Section \ref{directstyle}, we transform the refunctionalized AAM to two
different direct style, one is implemented with monads, the other is using
delimited controls.

@@

\section{Related Work}

@@

\section{Conclusion}

>>>>

The remainder of this paper is organized as follows.
We begin by describing the target language we will analyze in Section~\ref{background},
including a concrete CESK machine as small-step operational semantics for it.
We continue with a review of abstracting abstract machines (AAM) as an abstract interpretation
counterpart of CESK machines. Following this, Section~\ref{linear} shows a conversion from the
nondeterministic choices of closures to another layer of continuations,
therefore linearizing the abstract execution.
Section~\ref{fusing} then discusses fusing the driver and step functions to a single
function.
We further identify in Section~\ref{disen} the first-order data type representations of
continuations, and disentangle the code blocks for dispatching data types to separate
functions.
Section~\ref{refunc} then represents the refunctionalized abstract abstract machines.
In this section, the continuations represented by data types become higher-order
functions.
In Section~\ref{directstyle}, we transform the refunctionalized AAM to two
different direct style, one is implemented with monads, the other is using
delimited controls.

Finally, we discuss related work in Section~\ref{sec:related}, followed by concluding thoughts in Section~\ref{sec:conclusion}.

@@

\section{Related Work}\label{sec:related}

@@

\section{Conclusion}\label{sec:conclusion}
